A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-06-13 deprecated.tex
Add SaaS description

>>>>

Aware of the development of big data science, Radwa et. al.\cite{BigDataaaS} proposed the concept of big data science as a service framework which combines data resources, cloud computing platform and machine learning softwares as building blocks and makes them different subscription services. As more and more platforms and services release, interoperability is arising as a main issue. However, a data trading platform is still the missing piece which data and rewards are traded for innovation.

### 2020-06-13 paper.tex
Minor tweak
Add SaaS description

In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we proposed a novel data trading infrastructure which aims for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements. As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline. For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication. While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV. Therefore, a publish/subscribe model that provides the flexibility of following and unfollowing the data streams for users is more appropriate in the IoT scenarios.

Proving the identity as well as the ownership of data is a challenging issue among various roles and large scale of platform. In current systems, trusted third-party authority like CA is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}.

>>>>

%publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements. As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline. For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication. While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV. Therefore, the publish/subscribe (pub/sub) communication model that provides the flexibility of following and unfollowing the data streams for users is more appropriate in the IoT scenarios.

% SaaS
The economic incentive model in our proposed IoT data trading platform works as subscription service. The subscription-based models (e.g. software-as-a-service (SaaS) and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams. The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform. \cite{SaaS} pointed out that the strength of the relationships between consumers and providers depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.

%trustless
Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform. In current systems, trusted third-party authority like CA is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}.
